Air cargo load and route planning in pickup and delivery operations

### 2024-01-30 latex/eswa.tex
eswa updated and sent to Carlos

\usepackage{caption}
\captionsetup{labelfont=bf}
\captionsetup{skip=0pt}

@@

% lets get the exact color
\usepackage{xcolor}
\definecolor{myblue}{HTML}{B0D7FF}

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

	\centering
	\begin{tikzpicture}

		%% Make the boxes
		\node [mybox] (first)                        { \small {\bf Select:}\\ \small 1. scenario\\ \small 2. surplus\\ \small 3. time limit};
		\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ \small 4. parameters\\ \small 5. cost matrix\\ \small 6. pallets\\ \small 7. items};
		\node [mybox, right=0.7cm of second] (third) { \small {\bf Define tour}\\  \small {\bf schema:}\\ \small 8. All K! tours\\ \ \ \  \small or\\ \small 8. Solve a TSP\\ \small  \ \ \ (set of tours))};
		\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ \small 9. Many tours\\ \small  \ \ \ (node-by-node)\\ \small 10. Select best tour};

@@

	\end{tikzpicture} 
	\caption{Solution main flow}
	\label{fig:flow}
\end{figure}

@@

@@

	\item In the {\it greedy phase}\/ (lines \ref{shims:pallets}-\ref{shims:endfirst}), a partial solution for each pallet $i$\/ is constructed by adding edges following $\theta_{ij}$\/ order.
	The $\eta_1$\/ index corresponds to the accumulated volume equal to $V_i \times {\color{blue}threshold_1}$. In $\eta_2$\/ index, this same accumulated volume reaches $V_i \times  {\color{blue}threshold_2}$. {\color{blue}The values of these thresholds were defined empirically by the {\it iRace}\/ tool \citep{LopezIbanezManuel2016}}.

@@

{\color{blue}
	iRace (Iterated Racing for Automatic Algorithm Configuration) streamlines the tuning of optimization algorithms by iteratively testing and eliminating weaker parameter configurations through statistical comparisons. It focuses computational resources on the most promising settings. This method significantly cuts down the time and effort needed to find optimal or near-optimal parameters, proving effective across various application domains.
}

@@

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item $RandomInt(i_1,i_2)$: randomly selects a integer number in $[i_1,i_2]$, where $i_1$ and $i_2$ are integer numbers;
	\item $Roulette(set)$ biased through $\phi$: selects an element from $set$, where the probability of each element is proportional to the value of a given function $\phi$\/ defined on $set$.
\end{itemize}

@@

{\color{blue}
	After the items were generated, some experiments with the \textit{iRace} tool were executed to determine the values for parameters $threshold_1$ and $threshold_2$ used in \textit{Shims}, whose results are presented in Table \ref{tab:irace}.

	\begin{table}[H]
	\centering
	\caption{\textit{iRace} testing results}  \label{tab:irace}
	\footnotesize
	\begin{tabular}{cccc}
		\toprule

@@

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.
}

@@

\citep{PeerlinckAmy2022MFEO} applied DEAP to solve a Multi-Objective Knapsack Problem. This algorithm is adapted to solve the ACLPP in each node of this work's solution.

@@

We adopted some simplifications that are not critical, but that allowed for an unprecedented solution to this problem considering more than two nodes. In practical cases, the number $K$\/ of nodes, excluding the base, is small ($K \leq 6$), each of which has hundreds of items to be shipped. Considering a real aircraft, we have developed some node-by-node solutions. This allows us to test two strategies: find a solution using the shortest tours, or enumerate all $K!$\/ tours and choose the best. The complete process can be executed quickly on a handheld computer, offering good results and reducing stress for the transport planners.

>>>>

\usepackage{caption}
\captionsetup{labelfont=bf}
\captionsetup{skip=2pt}

@@

% lets get the exact color
\usepackage{xcolor}
\definecolor{myblue}{HTML}{D6EAF8} % A9CCE3  B0D7FF

\tikzset{
	mybox/.style={rectangle,
		draw,
		fill= myblue,
		rounded corners,
		minimum width=2cm,
		inner sep=5pt,
		align=left,
		minimum height=1cm
	},
	myarrow/.style={draw=black,
		fill=white,
		minimum width=0.6cm,
		single arrow
	},
	downarrow/.style={draw=black,
	fill=white,
	minimum width=0.6cm,
	single arrow
	},
	longarrow/.style={draw=none,
		shading=axis,
		left color=white,
		right color=myblue,
		minimum width=0.6cm,
		single arrow,
		anchor=east
	}
}

@@

	\centering
	\fbox{
	\begin{tikzpicture}

		%% Make the boxes
		\node [mybox] (first)                        { \small {\bf Select:}\\ 
			\small 1. scenario\\ 
			\small 2. surplus\\ 
			\small 3. time limit};

		\node [mybox, right=0.7cm of first] (second) { \small {\bf Config:}\\ 
			\small 4. parameters\\ \small 5. cost matrix\\ 
			\small 6. pallets\\ 
			\small 7. items};

		\node [mybox, right=0.7cm of second] (third) { \small {\bf Define tour}\\  
			\small {\bf schema:}\\ 
			\small 8. All K! tours\\ \ \ \  
			\small or\\ 
			\small 8. Solve a TSP\\ 
			\small  \ \ \ (set of tours))};

		\node [mybox, right=0.7cm of third] (fourth) { \small {\bf Solve ACLPP+RPDP:}\\ 
			\small 9. Many tours{\bf *}\\ 
			\small 10. Select best tour};

		\node [mybox, below=0.7cm of third] (fifth) { \small {\bf *Solve a tour:}\\
			\small \ \ \ {\it - For each node:}\\
			\small \ \ \ \ \ {a. Unload some pallets}\\
			\small \ \ \ \ \ {b. Arrange remaining pallets to balance cargo}\\
			\small \ \ \ \ \ {c. Set empty pallets destinations}\\
			\small \ \ \ \ \ {d. \it For each pallet:}\\
			\small \ \ \ \ \ \ \ \ \ {Solve an ACLPP with WBP and PDP constraints}\\
			\small \ \ \ \ \ {e. Calculate node score and torque}\\
			\small \ \ \ {\it - Return tour Score/Cost}

	};

@@

	\end{tikzpicture} 
}
	\caption{Solution main flow}
	\label{fig:flow}
\end{figure}

@@

As \citep{PeerlinckAmy2022MFEO} applied the DEAP (Distributed Evolutionary Algorithms in Python) to solve a Multi-Objective Knapsack Problem, we also decided to apply this evolutionary package to implement a GA solution for the ACLPP.

@@

	\item In the {\it greedy phase}\/ (lines \ref{shims:pallets}-\ref{shims:endfirst}), a partial solution for each pallet $i$\/ is constructed by adding edges following $\theta_{ij}$\/ order.
	The $\eta_1$\/ index corresponds to the accumulated volume equal to $V_i \times {\color{blue}threshold_1}$. In $\eta_2$\/ index, this same accumulated volume reaches $V_i \times  {\color{blue}threshold_2}$. {\color{blue}The values of these thresholds were defined empirically by the {\it irace}\/ tool \citep{LopezIbanezManuel2016}}.

@@

{\color{violet}
	{\it irace} (Iterated Racing for Automatic Algorithm Configuration) streamlines the tuning of optimization algorithms by iteratively testing and eliminating weaker parameter configurations through statistical comparisons. Its application may be understood, from a Machine Learning standpoint, as the task of identifying optimal parameter values for solving new problem instances by leveraging knowledge gained from a set of training problem examples. This method significantly cuts down on the time and effort needed to find optimal or near-optimal parameters, proving effective across various application domains.
}

@@

\begin{itemize}
	\setlength\itemsep{-0.3em}
	\item $RandomInt(i_1,i_2)$: randomly selects a integer number in $[i_1,i_2]$, where $i_1$ and $i_2$ are integer numbers;
{\color{violet}
\item $Roulette()$: a proportional selection function that is biased through $P$ (Table \ref{tab:weights}).
}
\end{itemize}

@@

{\color{blue}
	After the items were generated, some experiments with the \textit{irace} tool were executed to determine the values for parameters $threshold_1$ and $threshold_2$ used in \textit{Shims}, whose results are presented in Table \ref{tab:irace}.

	\begin{table}[H]
	\centering
	\caption{\textit{irace} testing results}  \label{tab:irace}
	\footnotesize
	\begin{tabular}{cccc}
		\toprule

@@

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{irace} runs. We supplied \textit{irace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{irace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{irace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.
}

@@

@@

{\color{blue}
We adopted some simplifications that are not critical, but that allowed for an unprecedented solution to this problem considering more than two nodes. In practical cases, the number $K$\/ of nodes, excluding the base, is small ($K \leq 6$), each of which has hundreds of items to be shipped. Considering a real aircraft, we have developed some node-by-node solutions. The complete process can be executed quickly on a handheld computer, offering good results and reducing stress for the transport planners.}
